---
layout: page
title: "ds001-rlang"
output:
  html_document: 
    theme: journal
    toc: yes
    toc_depth: 2
    toc_float: true
    highlight: tango
    code_folding: show
mainfont: NanumGothic
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE}
library(tidyverse)
library(DT)
```


일반적으로 많이 사용되는 라이선스

- The “GNU Affero General Public License” version 3
- The “Artistic License” version 2.0
- The “BSD 2-clause License”
- The “BSD 3-clause License”
- The “GNU General Public License” version 2
- The “GNU General Public License” version 3
- The “GNU Library General Public License” version 2
- The “GNU Lesser General Public License” version 2.1
- The “GNU Lesser General Public License” version 3
- The “MIT License”
- The “Creative Commons Attribution-ShareAlike International License” version 4.0




```{r data-science-license}
pkg_df <- installed.packages() %>% as_tibble()

pkg_df %>% mutate(
    license_chk = 
        case_when(
            str_detect(License, "GPL") ~ "GPL",
            str_detect(License, "MIT") ~ "MIT",
            str_detect(License, "Part of R 3.4.2") ~ "GPL",
            str_detect(License, "LGPL") ~ "LGPL",
            str_detect(License, "BSD") ~ "BSD",
            str_detect(License, "MPL") ~ "MPL",
            str_detect(License, "Apache") ~ "Apache",
            str_detect(License, "Unlimited|CC0|CC BY") ~ "CC",
            str_detect(License, "Lucent Public License") ~ "Lucent Public",
            str_detect(License, "file LICENSE") ~ "file LICENSE",
            str_detect(License, "BSL") ~ "Boost Software License"
        )
    ) %>% 
    count(license_chk, sort=TRUE) %>% 
    mutate(`비율` = n / sum(n),
           `누적비` = cumsum(`비율`)) %>% 
    select(`라이선스`=license_chk, `팩키지수`=n, everything()) %>%
	DT::datatable() %>% 
      formatPercentage(c("비율", "누적비"), digits=1)
```

팩키지에 대한 오픈소스 라이선스 구체적인 정보는 다음과 같다.

```{r data-science-license-detail}
pkg_df %>% 
    select(Package, Version, License, License_is_FOSS, Depends) %>% 
    datatable() 
```












